% pdflatex --shell-escape WRITEUP.tex

\documentclass[12pt]{article}
\usepackage{booktabs,fullpage,amsmath,minted,graphicx,fourier}

\title{Analysis -- A Little Slice of $\pi$}
\author{Giovanni Boccaccio}
\date{Fall 2021}

\begin{document}\maketitle

\section{Introduction}\label{intro}

Remember how long thou hast already put off these things, and how
often a certain day and hour as it were, having been set unto thee by
the gods, thou hast neglected it. It is high time for thee to understand
the true nature both of the world, whereof thou art a part; and of that
Lord and Governor of the world, from whom, as a channel from the spring,
thou thyself didst flow: and that there is but a certain limit of time
appointed unto thee, which if thou shalt not make use of to calm and
allay the many distempers of thy soul, it will pass away and thou with
it, and never after return.

\begin{quote}
Vivamus mea Lesbia, atque amemus, \\
rumoresque senum severiorum \\
omnes unius aestimemus assis! \\
soles occidere et redire possunt: \\
nobis cum semel occidit brevis lux, \\
nox est perpetua una dormienda. \\
da mi basia mille, deinde centum, \\
dein mille altera, dein secunda centum, \\
deinde usque altera mille, deinde centum. \\
dein, cum milia multa fecerimus, \\
conturbabimus illa, ne sciamus, \\
aut ne quis malus inuidere possit, \\
cum tantum sciat esse basiorum.
\end{quote}

\section{Code}\label{code}

\begin{minted}{python}
def is_prime_SS(n, k=100):
    """
    Solovay-Strassen probabilistic primality test of n with confidence k.
    """
    if n < 2 or (n != 2 and n % 2 == 0):
        return False
    if n < 4:
        return True
    for _ in range(0, k):
        a = uniform(2, n - 1) # Euler witness (or liar)
        x = Jacobi(a, n)
        if x == 0 or power_mod(a, (n - 1) // 2, n) != x % n:
            return False
    return True
\end{minted}

\section{Analysis}\label{analysis}

Vi\`{e}te's formula can be written as follows:
\[
  \frac{2}{\pi} = \frac{\sqrt{2}}{2} \times \frac{\sqrt{2 +
  \sqrt{2}}}{2} \times \frac{\sqrt{2 + \sqrt{2 + \sqrt{2}}}}{2} \cdots
\]

Or more simply,
\[
  \frac{2}{\pi} = \prod_{k=1}^{\infty} \frac{a_i}{2}
\]
where $a_1 = \sqrt{2}$ and $a_k = \sqrt{2 + a_{k-1}}$ for all $k > 1$.

\section{Conclusion}

\begin{table}[btp]
\centering
\caption{Example metadata server lookup table (MLT)}
\label{table:mlt}
\medskip
\begin{tabular}{cc}
\toprule
 Range of Hash Values & metadata server ID\\
 \midrule
 0--3FFE & 0\\
 3FFF--7FFD & 1\\
 7FFE--BFFC & 2\\
 BFFD--FFFB & 3\\
 \bottomrule
\end{tabular}
\end{table}

Poor Catullus, you must stop being silly,
and count as lost what you see is lost.
Once the sun shone bright for you,
when you would go whither your sweetheart led,
she who was loved by me as none will ever be loved.
Then there took place those many jolly scenes
which you desired nor did your sweetheart not desire.
Truly the sun shone bright for you.
Now she desires no more: do you too, weakling, not desire;
and do not chase her who flees, nor live in unhappiness,
but harden your heart, endure and stand fast.
Goodbye, sweetheart. Catullus now stands fast:
he will not look for you or court you against your will.
But you will be sorry when you are not courted at all.
Wretch, pity on you! What life lies in store for you!
Who will come to you now? Who will think you pretty?
Whom will you love now? Who will people say you are?
Whom will you kiss? Whose lips will you bite?
But you, Catullus, be resolute and stand fast.

\end{document}
